---
title: "Statistical Analysis Report"
author: "Statistical Analysis Results"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(knitr)
library(kableExtra)
```

# Introduction

This report presents the comprehensive statistical analysis results of various clinical parameters and their relationships with Total values.

# Data Summary

```{r}
# Read the data
data <- read.csv2("Test.csv")
```

## Basic Statistics

### Length of Stay vs Total
* Spearman's correlation coefficient (rho): `r round(cor.test(data$Total, data$Lenght.of.stay, method="spearman", exact=FALSE)$estimate, 3)`
* p-value: `r format.pval(cor.test(data$Total, data$Lenght.of.stay, method="spearman", exact=FALSE)$p.value, digits=3)`

### Follow-Up vs Total
* Spearman's correlation coefficient (rho): `r round(cor.test(data$Total, data$Follow.Up, method="spearman", exact=FALSE)$estimate, 3)`
* p-value: `r format.pval(cor.test(data$Total, data$Follow.Up, method="spearman", exact=FALSE)$p.value, digits=3)`

# Correlation Analysis Results

## Continuous Variables Correlations with Total

```{r}
# Function to perform correlation analysis and create a data frame
get_correlation_results <- function(data, var_name, var) {
  result <- cor.test(data[[var]], data$Total, method="spearman", exact=FALSE)
  data.frame(
    Variable = var_name,
    Correlation = round(result$estimate, 3),
    P_value = format.pval(result$p.value, digits=3)
  )
}

# List of variables to analyze
vars <- list(
  "Age" = "Age",
  "BMI" = "BMI",
  "Weight" = "Weight",
  "Duration" = "Duration",
  "Size" = "Size",
  "CRP" = "CRP",
  "Mamma 24h" = "Mamma.24h",
  "Axilla 24h" = "Axilla.24h",
  "pT (Tumor Size)" = "pT",
  "pN (Lymph Node Status)" = "pN",
  "N(X/x)" = "N.X.x.",
  "Length of Stay" = "Lenght.of.stay"
)

# Create results table
results <- do.call(rbind, lapply(names(vars), function(name) {
  get_correlation_results(data, name, vars[[name]])
}))

kable(results, 
      caption = "Spearman Correlations with Total",
      col.names = c("Variable", "Correlation Coefficient", "P-value"),
      align = c('l', 'c', 'c'))
```

# Categorical Variables Analysis

## ANOVA Results

### Total vs Histology (CNB)
```{r}
anova_hist <- aov(Total ~ factor(Histology..CNB.), data=data)
anova_summary <- summary(anova_hist)
```
* F-statistic: `r round(anova_summary[[1]]$"F value"[1], 3)`
* p-value: `r format.pval(anova_summary[[1]]$"Pr(>F)"[1], digits=3)`

### Total vs BRCA
```{r}
anova_brca <- aov(Total ~ factor(BRCA), data=data)
anova_summary <- summary(anova_brca)
```
* F-statistic: `r round(anova_summary[[1]]$"F value"[1], 3)`
* p-value: `r format.pval(anova_summary[[1]]$"Pr(>F)"[1], digits=3)`

## T-Test Results

### Total vs Diabetes
```{r}
t_test_diabetes <- t.test(Total ~ Diabetes, data=data)
```
* t-statistic: `r round(t_test_diabetes$statistic, 3)`
* p-value: `r format.pval(t_test_diabetes$p.value, digits=3)`
* Mean difference: `r round(diff(tapply(data$Total, data$Diabetes, mean, na.rm=TRUE)), 2)`

### Total vs Mastectomy
```{r}
t_test_mastectomy <- t.test(Total ~ Mastectomy, data=data)
```
* t-statistic: `r round(t_test_mastectomy$statistic, 3)`
* p-value: `r format.pval(t_test_mastectomy$p.value, digits=3)`
* Mean difference: `r round(diff(tapply(data$Total, data$Mastectomy, mean, na.rm=TRUE)), 2)`

# Summary of Key Findings

1. **Strong Correlations (|rho| > 0.5)**:
   - Length of Stay (rho = `r round(cor.test(data$Total, data$Lenght.of.stay, method="spearman", exact=FALSE)$estimate, 3)`)
   - Duration (rho = `r round(cor.test(data$Total, data$Duration, method="spearman", exact=FALSE)$estimate, 3)`)

2. **Moderate Correlations (0.3 < |rho| < 0.5)**:
   - Size (rho = `r round(cor.test(data$Total, data$Size, method="spearman", exact=FALSE)$estimate, 3)`)
   - BMI (rho = `r round(cor.test(data$Total, data$BMI, method="spearman", exact=FALSE)$estimate, 3)`)

3. **Significant Categorical Variables**:
   - Mastectomy (p = `r format.pval(t_test_mastectomy$p.value, digits=3)`)
   - BRCA status (p = `r format.pval(anova_summary[[1]]$"Pr(>F)"[1], digits=3)`)

# Conclusions

The analysis reveals several significant relationships with Total values:

1. Length of stay shows the strongest correlation with Total values
2. Several clinical parameters (Duration, Size, BMI) show moderate to strong correlations
3. Categorical variables like Mastectomy and BRCA status show significant associations with Total values

Note: All statistical tests were performed using Spearman correlation for continuous variables, t-tests for binary variables, and ANOVA for categorical variables with more than two levels. 